Pillar 2 - (STM) Topic Modeling

### 2019-03-28 Pillar 2 -(STM) Topic Modeling.Rmd
test fit new docs

For `d_text` we keep only the most recent year.
```{r import data, eval = TRUE}
#load
load("output/data_pillar_2.RDATA")

# keep most recent year
d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```

@@

>>>>

For `d_text` we keep only the most recent year.
```{r import data, eval = TRUE}
#load
#load("output/data_pillar_2.RDATA")
load("Output/d_text.RDATA")

# keep most recent year
#d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```

@@

#New Documents
##Align vocabulary
```{r align vocab}
#single case: Fasos topics
d_text1 <- d_text #backup current code

fasos_docs <- d_text$catalogues%>%filter(department == "European_studies") %>%
  select(-department)

fasos_cast <- my_cast_dtm(fasos_docs)

```
##Fit new docs
```{r}
model <- stm_model %>% filter(`Topic ID`=="overview_10")%>%
  pull(Model)

model <- model[[1]]

# fitting:
out <- asSTMCorpus(fasos_cast)

newdocs <- alignCorpus(new=out, old.vocab = model$vocab)

fasos_theta <- fitNewDocuments(model = model, documents=newdocs$documents) #returns a course by topic matrix

plot.STM(model, type ="summary")

fasos_theta$theta #nice kind of makes sense
